Context Inconsistency Management \\in Pervasive Systems

### 2011-04-23 paper/paper.tex
tweak

\section{Partial Constraint Checking}
Constraint checking techniques have been extensively studied in software engineering. Existing constraint checking algorithms focus on checking software artifacts that do not change rapidly or frequently~\cite{xu:2010:PCC}. Context-aware applications require more efficient algorithms because they use a huge set of contexts, which can change very rapidly and frequently (in the range of milliseconds). An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate. Because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}. One example of an inefficient approach is non-incremental checking: whenever there is a change in the set of software artifacts these artifacts are each checked against the entire set of consistency constraints to find out all detectable inconsistencies. An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set. But Xu et \textit{al.} made the most substantial progress by replacing the traditional entire constraint checking approach by partial constraint checking based on a consistency computation tree~\cite{xu:2010:PCC}. Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets. Whenever a context is added to or deleted from a context set in time, the branch corresponding to this context can respectively be added to or deleted from the tree (see Fig.~\ref{fig:cct}). 
\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{cons_comp_tree}
  \caption{Consistency Computation Tree: branches can be added or deleted to represent changes in a context set. Source:~\cite{xu:2010:PCC}}
  \label{fig:cct}
\end{figure}
Because intermediate values are retained in the tree nodes after calculation, they can be reused whenever the tree changes. More specifically, when a branch is added, only the values of the new branch itself and of the nodes from the branch top to the tree root need to be calculated. When a branch is deleted, only the values for the nodes from the branch top to the tree root have to be recalculated.

With their partial constraint checking algorithm Xu et \textit{al.} attained a time complexity between $O(n)$ in the worst case and $O(1)$ in the best case when a context is added to the set and $O(1)$ when a context is removed. Compared to traditional constraint checking with an overall complexity of $O(n)$, this is a dramatical improvement. In their experiments Xu et \textit{al.} showed their performance is 15 times better than the traditional approach and in a case study the inconsistency miss rate dropped from $52.2\%$ in traditional checking to $0.1\%$ with partial checking~\cite{xu:2010:PCC}.

\section{Context Inconsistency Resolution}
Now that we have an efficient method for detecting inconsistencies, the task of resolving the conflicts remains. As discussed above the strategies for conflict resolution in literature are not well suited for pervasive computing because their assumptions do not apply or they require human participation~\cite{xu:2010:PCC}. What is really needed is an algorithm that in the case of a conflict between two or more contexts decides which context has the highest reliability and retains that context. Bu et \textit{al.} show us that this is possible through extending the ontology based context model with additional information about the context's status and temporal properties~\cite{bu:2006:CCM}. More specifically they propose an algorithm that retains for every conflict set the context with the highest \textit{relative frequency}: frequency of context updates relative to update interval and context age (see Fig.~\ref{fig:cir}). 
\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{cir}
  \caption{Context inconsistency resolution in action. Source:~\cite{bu:2006:CCM}}
  \label{fig:cir}
\end{figure}
This is based on the assumption that contexts that are most stably perceived by a system are most likely to be correct. This assumption is applicable to most of the environments in which pervasive systems run and is applied in many domains as a domain specific approach~\cite{xu:2010:PCC}.

>>>>

\section{Partial Constraint Checking}
Constraint checking techniques have been extensively studied in software engineering. Existing constraint checking algorithms focus on checking software artifacts that do not change rapidly or frequently~\cite{xu:2010:PCC}. Context-aware applications require more efficient algorithms because they use a huge set of contexts, which can change very rapidly and frequently (in the range of milliseconds). An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate. Because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}. One example of an inefficient approach is non-incremental checking: whenever there is a change in the set of software artifacts these artifacts are each checked against the entire set of consistency constraints to find out all detectable inconsistencies. An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set. But Xu \textit{et al.} made the most substantial progress by replacing the traditional entire constraint checking approach by partial constraint checking based on a consistency computation tree~\cite{xu:2010:PCC}. Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets. Whenever a context is added to or deleted from a context set in time, the branch corresponding to this context can respectively be added to or deleted from the tree (see Fig.~\ref{fig:cct}). 
\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{cons_comp_tree}
  \caption{Consistency Computation Tree: branches can be added or deleted to represent changes in a context set. Source:~\cite{xu:2010:PCC}}
  \label{fig:cct}
\end{figure}
Because intermediate values are retained in the tree nodes after calculation, they can be reused whenever the tree changes. More specifically, when a branch is added, only the values of the new branch itself and of the nodes from the branch top to the tree root need to be calculated. When a branch is deleted, only the values for the nodes from the branch top to the tree root have to be recalculated.

With their partial constraint checking algorithm Xu \textit{et al.} attained a time complexity between $O(n)$ in the worst case and $O(1)$ in the best case when a context is added to the set and $O(1)$ when a context is removed. Compared to traditional constraint checking with an overall complexity of $O(n)$, this is a dramatical improvement. In their experiments Xu \textit{et al.} showed their performance is 15 times better than the traditional approach and in a case study the inconsistency miss rate dropped from $52.2\%$ in traditional checking to $0.1\%$ with partial checking~\cite{xu:2010:PCC}.

\section{Context Inconsistency Resolution}
Now that we have an efficient method for detecting inconsistencies, the task of resolving the conflicts remains. As discussed above the strategies for conflict resolution in literature are not well suited for pervasive computing because their assumptions do not apply or they require human participation~\cite{xu:2010:PCC}. What is really needed is an algorithm that in the case of a conflict between two or more contexts decides which context has the highest reliability and retains that context. Bu \textit{et al.} show us that this is possible through extending the ontology based context model with additional information about the context's status and temporal properties~\cite{bu:2006:CCM}. More specifically they propose an algorithm that retains for every conflict set the context with the highest \textit{relative frequency}: frequency of context updates relative to update interval and context age (see Fig.~\ref{fig:cir}). 
\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{cir}
  \caption{Context inconsistency resolution in action. Source:~\cite{bu:2006:CCM}}
  \label{fig:cir}
\end{figure}
This is based on the assumption that contexts that are most stably perceived by a system are most likely to be correct. This assumption is applicable to most of the environments in which pervasive systems run and is applied in many domains as a domain specific approach~\cite{xu:2010:PCC}.
